West Africa cuckoo stopover rainfall patterns

### 2018-09-17 gd_cuck_plots.Rmd

dat<-read.csv("~/BTO/cuckoo_tracking/data/stopover_bestofday_spring_mig.csv", h=T)

dat2<-read.csv("~/BTO/cuckoo_tracking/data/processed_movebank_cuckoos_hybrid_filter_clean_stopovers.csv", h=T)

UK_travel<-read.csv("~/BTO/cuckoo_tracking/data/complete_cycles_UK_all_timing.csv", h=T)

@@

@@

for(i in unique(dat3$ptt))
{
  cols <- c("2012" = "red", "2013" = "blue", "2014" = "darkgreen", "2015" = "orange", "2016"= "cyan", "2017"= "black")

  g<-ggmap(m1)+
    geom_path(data=dat3[dat3$ptt==i,], aes(x=long, y=lat,
                                             colour=factor(year.x)))+
    geom_jitter(data=dat3[dat3$ptt==i,], aes(x=long, y=lat,
                colour=factor(year.x)), shape=1, width = 0.5, height= 0.5)+ggtitle(i)+

  geom_label_repel(data=dat[dat$ptt==i & dat$deployment_entry==FALSE,], aes(x=SO_median_long, y=SO_median_lat,
                colour=factor(year), label=substr(SO_start, 6,10)))+
  geom_label_repel(data=aggregate(year~breeding_entry, data=dat[dat$ptt==i & dat$deployment_entry==FALSE,], FUN=function(x){unique(x)})
                   , aes(x=-18, y=45,
                colour=factor(year), label=unique(substr(breeding_entry, 6,10)))) + scale_colour_manual(values = cols)

>>>>

dat<-read.csv("C:/cuckoo_tracking/data/stopover_bestofday_2018_1daymin_recalc_spring_mig.csv", h=T)

dat2<-read.csv("C:/cuckoo_tracking/data/processed_movebank_cuckoos_hybrid_filter_2018_clean_stopovers_recalc.csv", h=T)

UK_travel<-read.csv("C:/cuckoo_tracking/data/complete_cycles_UK_all_timing.csv", h=T)

@@

names(dat3)[names(dat3)=='year.x']<-'year'

@@

for(i in unique(dat3$ptt))
{
  cols <- c("2012" = "red", "2013" = "blue", "2014" = "darkgreen", "2015" = "orange", "2016"= "cyan", "2017"= "black",
            "2018"= "purple")

  g<-ggmap(m1)+
    geom_path(data=dat3[dat3$ptt==i,], aes(x=long, y=lat,                                      colour=factor(year)))+
    geom_jitter(data=dat3[dat3$ptt==i,], aes(x=long, y=lat,
                colour=factor(year)), shape=1, width = 0.5, height= 0.5)+ggtitle(i)+

  geom_label_repel(data=dat[dat$ptt==i & dat$deployment_entry==FALSE,], aes(x=SO_median_long, y=SO_median_lat,
                colour=factor(year), label=substr(SO_start, 6,10)))+
  geom_label_repel(data=aggregate(year~breeding_entry, data=dat[dat$ptt==i,], FUN=function(x){unique(x)})
                   , aes(x=-18, y=45,
                colour=factor(year), label=substr(breeding_entry, 6,10))) + scale_colour_manual(values = cols)

### 2018-09-17 stopover_rainfall_vis.Rmd

int_out<-read.csv('data/spring_rainfall_NDVI_by_stopover_2018_dead.csv', h=T)

@@

for( i in 2012:2017)
  {
  int1<-int_out[int_out$year==i,]

@@

temp=ggplot(data=t2,aes(x=variable, y=value))+
geom_rect(aes(xmin=SO_startDOY, xmax=SO_endDOY, ymin=0, ymax=500), fill='grey')+
    geom_bar(data=t2, aes(x=variable, y=value2*500, group=1), stat='identity', fill='red', linetype=0, alpha=1/3)+
  geom_bar(stat='identity', colour='black')+
    geom_line(aes(y=cumrf), col='green', size=1)+
  facet_wrap(~country+SO_startDOY, scales='free_y')+theme_classic()+
  ylab('cumulative rainfall since 01 Jan (mm)')+ xlab('Day of year')+
          ggtitle(paste("Year:",i,"   PTT:", j, "   Arr date:", dtemp$arrive_breeding))

>>>>

int_out<-read.csv('data/spring_rainfall_NDVI_GRIMMS_by_stopover_2018_dead.csv', h=T)

@@

for( i in 2012:2018)
  {
  int1<-int_out[int_out$year==i,]

@@

temp=ggplot(data=t2,aes(x=variable, y=value))+
geom_rect(aes(xmin=SO_startDOY, xmax=SO_endDOY, ymin=0, ymax=500), fill='grey')+
    geom_line(data=t2, aes(x=variable, y=value2*500), colour='red')+
  geom_line(data=t2, aes(x=variable, y=aquaNDVI*500), colour='cyan')+
  geom_line(data=t2, aes(x=variable, y=terrNDVI*500), colour='orange')+
  geom_bar(stat='identity', colour='black')+
    geom_line(aes(y=cumrf), col='green', size=1)+
  facet_wrap(~country+SO_startDOY, scales='free_y')+theme_classic()+
  ylab('cumulative rainfall since 01 Jan (mm)')+ xlab('Day of year')+
          ggtitle(paste("Year:",i,"   PTT:", j, "   Arr date:", dtemp$arrive_breeding))
